---
title: "Complete example"
output: pdf_document
vignette: >
  %\VignetteIndexEntry{Complete example}
  %\VignetteEncoding{UTF-8}
  %\VignetteEngine{knitr::rmarkdown}
editor_options: 
  chunk_output_type: console
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette contains all the code behind the example in the Journal of Open Source Software paper. This can be considered a real life application, so it contains a lot of code from different files in `inst/worklow` in the package directory and does not omit any code for data preparation, manipulation or plotting. See the package README for a minimal Quickstart guide instead.

```{r, echo = FALSE}
code_files_full_path <- list.files(
  system.file("workflow_example", package = "bleiglas", mustWork = T),
  pattern = ".R$", full.names = T
)
code_files <- basename(code_files_full_path)
sourcecode <- lapply(code_files_full_path, function(x) { paste(readLines(x), collapse="\n") })
```

## `r code_files[1]`

```{r eval=FALSE, code=sourcecode[[1]]}
```

## `r code_files[2]`

```{r eval=FALSE, code=sourcecode[[2]]}
```

## `r code_files[3]`

```{r eval=FALSE, code=sourcecode[[3]]}
```

## `r code_files[4]`

```{r eval=FALSE, code=sourcecode[[4]]}
```

## `r code_files[5]`

```{r eval=FALSE, code=sourcecode[[5]]}
```

## `r code_files[6]`

```{r eval=FALSE, code=sourcecode[[6]]}
```

## `r code_files[7]`

```{r eval=FALSE, code=sourcecode[[7]]}
```
